### 2022-12-10 dissertation/chapters/01-introduction.tex
Spacing configuration

\Acf{ML} is one of the most popular fields of research in \acf{AI} studies today. In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:vaswani:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver2017, ref:zoph:2017, ref:lewis:2017}.  \acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:silver:2017}.

>>>>

\Acf{ML} is one of the most popular fields of research in \acf{AI} studies today. In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:vaswani:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:silver:2017}.

### 2022-12-10 dissertation/chapters/02-artificial-neural-networks.tex
Spacing configuration

\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $omega_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution. Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.

@@

\begin{figure}[htb]
      \centering
      \includegraphics[width=0.65\textwidth]{output_modifiers.pdf}
      \caption[The results of \index{softmax}softmax and \index{argmax}argmax]{An illustration of \index{softmax}softmax and \index{argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}
      \label{fig:anns:activation_functions:softmax_argmax}
\end{figure}

>>>>

\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $\omega_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution. Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.

@@

\begin{figure}[htb]
      \centering
      \includegraphics[width=0.75\textwidth]{output_modifiers.pdf}
      \caption[The results of \index{softmax}softmax and \index{argmax}argmax]{An illustration of \index{softmax}softmax and \index{argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}
      \label{fig:anns:activation_functions:softmax_argmax}
\end{figure}

### 2022-12-10 dissertation/chapters/03-heuristics.tex
Spacing configuration

The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, while the update step is then amended in Equation~\eqref{eq:heuristics:gd:momentum_part_2}.

\begin{equation}
	\label{eq:heuristics:gd:momentum_part_1}
	\begin{split}
		\boldsymbol{v} = \alpha \boldsymbol{v} - \eta \boldsymbol{g}
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:heuristics:gd:momentum_part_2}
	\begin{split}
		\boldsymbol{w} = \boldsymbol{w} + \boldsymbol{v}
	\end{split}
\end{equation}

@@

\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space. This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position. In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}. The idea behind velocity clamping is to restrict particle velocities to some $\boldsymbol{V_{max}{}$ threshold, modelling a form of terminal velocity. Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.

>>>>

The accumulation of momentum is given as

\begin{equation}
	\boldsymbol{v} = \alpha \boldsymbol{v} - \eta \boldsymbol{g}
	\label{eq:heuristics:gd:momentum_part_1}
\end{equation}

while the update step is then amended as

\begin{equation}
	\boldsymbol{w} = \boldsymbol{w} + \boldsymbol{v}
	\label{eq:heuristics:gd:momentum_part_2}
\end{equation}

@@

\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space. This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position. In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}. The idea behind velocity clamping is to restrict particle velocities to some $\boldsymbol{V_{max}}$ threshold, modelling a form of terminal velocity. Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.
